---
title: "Anomaly detection based on depth functions"
author: "Hassan Maissoro"
date: "24/08/2021"
output: 
  html_document:
    toc : true
    toc_depth : 4
    number_sections: false
    theme: readable
    highlight: tango
    toc_float:
      collapsed: false
      smooth_scroll: false
    css: style.css
    fig_width: 6.5
    fig_height: 5
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      message = FALSE, eval = TRUE,
                      tidy = FALSE, cache = FALSE, echo = FALSE)
```

<!-- # Packages, functions and data -->

<!-- ## Import packages -->
```{r}
# Packages
packages <- list('data.table', 'DT', 'crosstalk', 'grDevices',
                 'rAmCharts', 'magrittr', 'manipulateWidget',
                 'leaflet', 'leaflet.minicharts', 'plotly')

invisible(lapply(packages, library, character.only = TRUE))
```

<!-- ## Import functions -->
```{r, include = FALSE}
functions_path <- '/home/hmaissoro/Stage/functionnal_data_analysis/anomaly_detection/R/'
```

```{r}
# Functions
lapply(list.files(functions_path,
                  recursive = T, full.names = T, pattern = ".R$|.r$"), function(X) {
                    source(X, encoding = 'UTF-8')
                  }) %>% invisible
```

## Import data
```{r, include = FALSE}
data_path <- '/home/hmaissoro/Stage/functionnal_data_analysis/anomaly_detection/data/'
```

```{r}
# Data
dt_fdc_ws <- readRDS(paste0(data_path, "dt_fdc_ws.rds", sep = ""))

fdc <- data.table::dcast(data = dt_fdc_ws[, .(id_prod, date, FDC)],
                         formula = id_prod ~ date, value.var = "FDC")
```


```{r}
# Plot 4 random load ratio curves
id_parc <- unique(dt_fdc_ws[, id_prod])
random_index <- sample(x = 1:length(id_parc), 4)

# Curve 1
curve_1 <- dyplotTimeSeries(data = dt_fdc_ws, id_parc = id_parc[random_index[1]], 
                            col_date = "date", col_series = "FDC",
                            group = "random-fdc")

# Curve 2
curve_2 <- dyplotTimeSeries(data = dt_fdc_ws, id_parc = id_parc[random_index[2]], 
                            col_date = "date", col_series = "FDC", color = "#900C3F",
                            group = "random-fdc")

# Curve 3
curve_3 <- dyplotTimeSeries(data = dt_fdc_ws, id_parc = id_parc[random_index[3]], 
                            col_date = "date", col_series = "FDC", color = "#FFC300",
                            group = "random-fdc")
# Curve 4
curve_4 <- dyplotTimeSeries(data = dt_fdc_ws, id_parc = id_parc[random_index[4]], 
                            col_date = "date", col_series = "FDC", color = "#08B11F",
                            group = "random-fdc")
# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(curve_1, curve_2, curve_3, curve_4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")
```


# Anomaly detection

To detect atypical curves, we are going to apply the following algorithm proposed by Horvàth and Kokoszka (2012)

<ul>
<li> <b> Step 1</b> : Compute Tukey and Simplicial depths on load ratio curves collection </li>
<li> <b> Step 2</b> : Fix a threshold Q. All curves with depth values (Tukey and/or Simplicial) lower than Q are considered atypical. If the number of curves in collection is low stop at this step.</li>
<li> <b> Step 3</b> : Go back to the first step without the atypical curves detected previously. </li>
</ul>

If there exists an exogenous variable
<ul>
<li> <b> Step 4</b> : Estimate functional linear model linking the cleaned collection of curves to the exogenous variable </li>
<li> <b> Step 5</b> : Exact residual curves</li>
<li> <b> Step 3</b> : Apply <b> Step 1, 2 & 3</b> on the collection of residual curves. </li>
</ul>

The aim of using Tukey and simplicial depth functions is to have an idea in the agreement of two different depth functions to detect atypical curves and the most depthest curve in a collection of curves.

<hr>

<div class="an-detect-1">

## Step 1 : Compute depths

```{r}
#Tukey and Simplicial depths
f_tukey_depth <- fdc[, -c("id_prod")] %>% functional_tukey_depth()

f_sdepth <- fdc[, -c("id_prod")] %>% functional_simplicial_depth()

fdc_depths <- data.table(id_prod = fdc[, id_prod],
                         tdepth = f_tukey_depth,
                         sdepth = f_sdepth)
```

```{r}
datatable(fdc_depths,
          options = list(pageLength = 5, autoWidth = TRUE, columnDefs = list(list(className = 'dt-center', targets = 0:2))),
          colnames = c("Wind farm identifier", "Tukey depth", "Simplicial depth"),
          rownames = FALSE)
```

## Step 2 : Atypical curves detection

```{r chunk-depth-elbow}

# Tukey depth
tplot <- plotDepth(data = fdc_depths, col_id = "id_prod", col_depth = "tdepth",
                   ylim = c(0, 0.35))

# Simpliciale depth
splot <- plotDepth(data = fdc_depths, col_id = "id_prod", 
                   col_depth = "sdepth", col = "#ad1b0e",
                   ylim = c(0, 0.45))

manipulateWidget::combineWidgets(list = list(tplot, splot), 
                                 ncol = 2,
                                 height = "300px",
                                 width = "800px")
```

<!-- # Commenter les courbes ci-dessus
     # NB : add button to dynamise the threshold
-->




```{r chunk-depth-analysis}
# Round to 4 digits
fdc_depths[, c("tdepth", "sdepth") := .(round(tdepth, 4), round(sdepth, 4))]

# Construct a crosslak::SharedData
fdc_depthsSharedData <- SharedData$new(fdc_depths)

bscols(widths = c(4,NA),
       list(
         filter_slider(id = "TukeyDepthThreshold", 
                       label = "Tukey depth", 
                       sharedData = fdc_depthsSharedData, 
                       column = ~tdepth,
                       step=0.001,
                       width=200,
                       round = 3),
         filter_slider(id = "SimplicialDepthThreshold", 
                       label = "Simplicial depth", 
                       sharedData = fdc_depthsSharedData, 
                       column = ~sdepth, 
                       step=0.001,
                       width=200,
                       round = 3)
       ),
       datatable(fdc_depthsSharedData,
                 options = list(pageLength = 10,
                                columnDefs = list(list(className = 'dt-center', targets = 0:2)),
                                scroller=TRUE, 
                                deferRender=TRUE, 
                                scrollY=300, 
                                sDom  = '<"top">lrt<"bottom">ip'),
                 colnames = c("Wind farm ID", "Tukey depth", "Simplicial depth"),
                 rownames = FALSE,
                 extensions="Scroller",  
                 class="compact", 
                 style="bootstrap", 
                 width="100%")
)
```

```{r}
# Depthest curve
DepthestCurve <- dyplotTimeSeries(data = dt_fdc_ws,
                                  id_parc = "478234", 
                                  main = "Wind farm '478234' : Most depthest curve",
                                  col_date = "date", 
                                  col_series = "FDC",
                                  color = "#08B11F",
                                  group = "random-step1")

# Curve 1
MostAtypical_1 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "551629", 
                                   main = "Wind farm '551629' : Most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC",
                                   group = "random-step1")

# Curve 2
MostAtypical_2  <- dyplotTimeSeries(data = dt_fdc_ws, 
                                    id_parc = "137668", 
                                    main = "Wind farm '137668' : Second most externe curve",
                                    col_date = "date", 
                                    col_series = "FDC", 
                                    color = "#900C3F",
                                    group = "random-step1")

# Curve 3
MostAtypical_3 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "534693",
                                   main = "Wind farm '534693' : Third most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#FFC300",
                                   group = "random-step1")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(DepthestCurve, 
                                             MostAtypical_1, 
                                             MostAtypical_2, 
                                             MostAtypical_3), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```






<!--Toutes les courbes atypiques on un problème lié à la Puissance Installée (PI) -->

Three wind farms are considered atypical at this stage. Their identifiers are "551629", "137668" and "534693".
<hr>
</div>
<div class="an-detect-2">
## Step 3 : back to step 1

<!-- {.tabset .tabset-fade .tabset-pills} -->

```{r}
# Remove the atypical curves detected previously
fdc_FirstCleaning <- fdc[! id_prod %in% c("551629", "137668", "534693"), ]
```

### Step 1 bis : Compute depths again

```{r}
#Tukey and Simplicial depths
f_tukey_depth <- fdc_FirstCleaning[, -c("id_prod")] %>% functional_tukey_depth()

f_sdepth <- fdc_FirstCleaning[, -c("id_prod")] %>% functional_simplicial_depth()

# Combine depths in data.table
fdc_depths <- data.table(id_prod = fdc_FirstCleaning[, id_prod],
                         tdepth = f_tukey_depth,
                         sdepth = f_sdepth)
```

### Step 2 bis : detect anomaly

<!-- Voir s'il y a pas une meilleure option -->
```{r ref.label=c('chunk-depth-elbow'), echo = FALSE}

```

```{r ref.label=c('chunk-depth-analysis'), echo = FALSE}

```

<!-- According to Tukey depth... visible problem for simplicial depth -->

```{r, echo = FALSE, eval=FALSE}

# Curve 1
MostAtypical_1 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "16465", 
                                   main = "Wind farm '16465' : Most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC",
                                   group = "random-step1-bis")

# Curve 2
MostAtypical_2  <- dyplotTimeSeries(data = dt_fdc_ws, 
                                    id_parc = "51867", 
                                    main = "Wind farm '51867' : Second most externe curve",
                                    col_date = "date", 
                                    col_series = "FDC", 
                                    color = "#900C3F",
                                    group = "random-step1-bis")

# Curve 3
MostAtypical_3 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "144482",
                                   main = "Wind farm '144482' : Third most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#FFC300",
                                   group = "random-step1-bis")

# Curve
MostAtypical_4 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "436002", 
                                   main = "Wind farm '436002' : fourth most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#08B11F",
                                   group = "random-step1-bis")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(MostAtypical_1, 
                                             MostAtypical_2, 
                                             MostAtypical_3, 
                                             MostAtypical_4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```



```{r, eval=FALSE}
ax <- list(
  title = "",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = TRUE,
  showgrid = FALSE
)
# Plot depth contour

df <- dt_fdc_ws[id_prod %in% "51867", .(id_prod, date, FDC)]

df <- df[, c("time", 
             "tdepth", 
             "sdepth") := .(difftime(date, as.POSIXct("2017-01-01 00:00:00 GMT"), units = "hours"),
                            tukey_depth(FDC),
                            simplicial_depth(FDC))
]

convex.hull0.25 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.25), 
                                          floor(length(FDC)*0.25),
                                          floor(length(FDC)*0.25) +1 )][chull(FDC)]

convex.hull0.5 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5) +1 )][chull(FDC)]
convex.hull0.75 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75) +1 )][chull(FDC)]
convex.hull0.975 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975) +1 )][chull(FDC)]

p <- plot_ly(data = df, x= ~time, y = ~FDC, type = "scatter",
        marker = list(size = 4, color = ~tdepth),
        name = "Observed FDC"
) %>%
  layout(
    xaxis = ax,
    yaxis = ax,
    margin = list(pad = 20),
    legend = list(orientation = 'h')
  )


dc1 <- p %>% 
  add_polygons(x = convex.hull0.25[, time], 
               y = convex.hull0.25[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#111613 ",
                             line = list(color = "black", width = 2)),
               line = list(color = "#111613"),
               name = '0.25 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc2 <- p %>% 
  add_polygons(x = convex.hull0.5[, time], 
               y = convex.hull0.5[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#FFC300",
                             line = list(color = "black", width = 2)),
               line = list(color = "#FFC300"),
               name = '0.5 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")


dc3 <- p %>% 
  add_polygons(x = convex.hull0.75[, time], 
               y = convex.hull0.75[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#7D3C98",
                             line = list(color = "black", width = 2)),
               line = list(color = "#7D3C98"),
               name = '0.75 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc4 <- p %>% 
  add_polygons(x = convex.hull0.975[, time], 
               y = convex.hull0.975[, FDC],
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#15EE6E",
                             line = list(color = "black", width = 2)),
               line = list(color = "#15EE6E"),
               name = '0.975 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(dc1, dc2, dc3, dc4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```
<hr>
</div>
<div class="an-detect-3">
### Step 3 bis : back to step 1

<!-- {.tabset} -->

```{r}
# Remove the atypical curves detected previously
fdc_SecondCleaning <- fdc_FirstCleaning[! id_prod %in% c("16465", "51867", "144482", "436002"), ]
```

#### Step 1 ter : compute depths

```{r}
#Tukey and Simplicial depths
f_tukey_depth <- fdc_SecondCleaning[, -c("id_prod")] %>% functional_tukey_depth()

f_sdepth <- fdc_SecondCleaning[, -c("id_prod")] %>% functional_simplicial_depth()

# Combine depths in data.table
fdc_depths <- data.table(id_prod = fdc_SecondCleaning[, id_prod],
                         tdepth = f_tukey_depth,
                         sdepth = f_sdepth)
```

#### Step 2 ter : detect anomaly

<!-- Voir s'il y a pas une meilleure option -->

```{r ref.label=c('chunk-depth-elbow'), echo = FALSE}

```

```{r ref.label=c('chunk-depth-analysis'), echo = FALSE}

```

<!-- According to Tukey depth... visible problem for simplicial depth -->

```{r, echo = FALSE, eval=FALSE}

# Curve 1
MostAtypical_1 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "404797", 
                                   main = "Wind farm '404797' : Most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC",
                                   group = "random-step1-ter")

# Curve 2
MostAtypical_2  <- dyplotTimeSeries(data = dt_fdc_ws, 
                                    id_parc = "42930", 
                                    main = "Wind farm '42930' : Second most externe curve",
                                    col_date = "date", 
                                    col_series = "FDC", 
                                    color = "#900C3F",
                                    group = "random-step1-ter")

# Curve 3
MostAtypical_3 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "46895",
                                   main = "Wind farm '46895' : Third most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#FFC300",
                                   group = "random-step1-ter")

# Curve
MostAtypical_4 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "139348", 
                                   main = "Wind farm '139348' : fourth most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#08B11F",
                                   group = "random-step1-ter")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(MostAtypical_1, 
                                             MostAtypical_2, 
                                             MostAtypical_3, 
                                             MostAtypical_4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```



```{r, eval=FALSE}
# Plot depth contour

df <- dt_fdc_ws[id_prod %in% "42930", .(id_prod, date, FDC)]

df <- df[, c("time", 
             "tdepth", 
             "sdepth") := .(difftime(date, as.POSIXct("2017-01-01 00:00:00 GMT"), units = "hours"),
                            tukey_depth(FDC),
                            simplicial_depth(FDC))
]

convex.hull0.25 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.25), 
                                          floor(length(FDC)*0.25),
                                          floor(length(FDC)*0.25) +1 )][chull(FDC)]

convex.hull0.5 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5) +1 )][chull(FDC)]
convex.hull0.75 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75) +1 )][chull(FDC)]
convex.hull0.975 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975) +1 )][chull(FDC)]

p <- plot_ly(data = df, x= ~time, y = ~FDC, type = "scatter",
        marker = list(size = 4, color = ~tdepth),
        name = "Observed FDC"
) %>%
  layout(
    xaxis = ax,
    yaxis = ax,
    margin = list(pad = 20),
    legend = list(orientation = 'h')
  )


dc1 <- p %>% 
  add_polygons(x = convex.hull0.25[, time], 
               y = convex.hull0.25[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#111613 ",
                             line = list(color = "black", width = 2)),
               line = list(color = "#111613"),
               name = '0.25 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc2 <- p %>% 
  add_polygons(x = convex.hull0.5[, time], 
               y = convex.hull0.5[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#FFC300",
                             line = list(color = "black", width = 2)),
               line = list(color = "#FFC300"),
               name = '0.5 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")


dc3 <- p %>% 
  add_polygons(x = convex.hull0.75[, time], 
               y = convex.hull0.75[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#7D3C98",
                             line = list(color = "black", width = 2)),
               line = list(color = "#7D3C98"),
               name = '0.75 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc4 <- p %>% 
  add_polygons(x = convex.hull0.975[, time], 
               y = convex.hull0.975[, FDC],
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#15EE6E",
                             line = list(color = "black", width = 2)),
               line = list(color = "#15EE6E"),
               name = '0.975 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(dc1, dc2, dc3, dc4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```


#### Step 3 ter : Stop here
<hr>
</div>
<div class="an-detect-res">

## Step 4 : Estimate de linear model

<ul>
<li> <b> Dpendent Variable </b> : Load profile curves ;</li>
<li> <b> Independent Variable</b> : Wind speed at 100m ;</li> <br>

<li> <b>Purpose </b> : Detect anomaly on the collection of residual curves. </li>
</ul>

```{r}
# Get the collection of cleaned curves
dt_fdc_ws <- dt_fdc_ws[! id_prod %in% c("551629", "137668", "534693", "16465", "51867", "144482", "436002"), ]
```

```{r}
setnames(dt_fdc_ws, c("LON", "LAT", "lon", "lat"), c("lon_parc", "lat_parc", "lon_ws", "lat_ws"))

```


### Matching Parc - Station méto
```{r}

dt_loc_parc <- unique(dt_fdc_ws[, .(lon_parc, lat_parc, lon_ws, lat_ws), by = id_prod])
dt_loc_ws <- unique(dt_fdc_ws[, .(lon_ws, lat_ws), by = id_ws.x])

## Faire une carte leaflet
leaflet() %>% 
  addTiles() %>% 
  setView(lng = 2.80, lat = 46.80, zoom = 5) %>% 
  addCircleMarkers(lng = dt_loc_parc[, lon_parc],
                   lat = dt_loc_parc[, lat_parc],
                   radius = 3,
                   weight = 2,
                   opacity = 0.8) %>% 
  addCircleMarkers(lng = dt_loc_ws[, lon_ws],
                   lat = dt_loc_ws[, lat_ws],
                   color = "red",
                   radius = 3,
                   weight = 2,
                   opacity = 0.8) %>% 
  addLegend(position = c("topright"), 
            colors = c("blue", "red"),
            labels = c("Parc éolien", "Station météo"),
            title = "Légende") %>% 
  addFlows(dt_loc_parc[, lon_parc],
           dt_loc_parc[, lat_parc],
           dt_loc_parc[, lon_ws],
           dt_loc_parc[, lat_ws], dir = 0, maxThickness = 2
  )
```

<!-- Quelques scatter plots -->

```{r}
# Plot 4 random load ratio curves
id_parc <- unique(dt_fdc_ws[, id_prod])
random_index <- sample(x = 1:length(id_parc), 4)

 
sp1 <- plot_ly(data = dt_fdc_ws[id_prod %in% id_parc[random_index[1]], .(id_prod, FDC, wind_sp_100)], 
               x= ~wind_sp_100, 
               y = ~FDC, 
               type = "scatter",
               marker = list(size = 5)
)%>%
  layout(
    title = paste("Wind farm", id_parc[random_index[1]]),
    xaxis = list(title = "Wind speed at 100m", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    yaxis = list(title = "Load profile", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    margin = list(pad = 20)
  )

sp2 <- plot_ly(data = dt_fdc_ws[id_prod %in% id_parc[random_index[2]], .(id_prod, FDC, wind_sp_100)], 
               x= ~wind_sp_100, 
               y = ~FDC, 
               type = "scatter",
               marker = list(size = 5, color = "#900C3F")
)%>%
  layout(
    title = paste("Wind farm", id_parc[random_index[2]]),
    xaxis = list(title = "Wind speed at 100m", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    yaxis = list(title = "Load profile", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    margin = list(pad = 20)
  )

sp3 <- plot_ly(data = dt_fdc_ws[id_prod %in% id_parc[random_index[3]], .(id_prod, FDC, wind_sp_100)], 
               x= ~wind_sp_100, 
               y = ~FDC, 
               type = "scatter",
               marker = list(size = 5, color = "#FFC300")
)%>%
  layout(
    title = paste("Wind farm", id_parc[random_index[3]]),
    xaxis = list(title = "Wind speed at 100m", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    yaxis = list(title = "Load profile", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    margin = list(pad = 20)
  )

sp4 <- plot_ly(data = dt_fdc_ws[id_prod %in% id_parc[random_index[4]], .(id_prod, FDC, wind_sp_100)], 
               x= ~wind_sp_100, 
               y = ~FDC, 
               type = "scatter",
               marker = list(size = 5, color = "#08B11F")
)%>%
  layout(
    title = paste("Wind farm", id_parc[random_index[4]]),
    xaxis = list(title = "Wind speed at 100m", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    yaxis = list(title = "Load profile", 
                 zeroline = FALSE, 
                 showline = FALSE, 
                 showticklabels = TRUE, 
                 showgrid = FALSE),
    margin = list(pad = 20)
  )

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(sp1, sp2, sp3, sp4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")




```



### Estimate linear model

```{r, echo = FALSE}
# --- Modèle linéaire --- #

# variable dépendante : FDC
# variable indépendante : vind_sp_100

fdc <- data.table::dcast(data = dt_fdc_ws[, .(id_prod, date, FDC)],
                         formula = id_prod ~ date, value.var = "FDC")

wind_sp <- data.table::dcast(data = dt_fdc_ws[, .(id_prod, date, wind_sp_100)],
                             formula = id_prod ~ date, value.var = "wind_sp_100")


# --- Lissage des courbes avec des paramètres par defaut --- #

## Base de fourier
fb <- create.fourier.basis(rangeval = c(1, 365*24), nbasis =  1780)

## 1) Lissage
fdc.fd <- Data2fd(argvals = 1:(365*24), y = t(fdc[, -1]),
                  lambda = 10,
                  basisobj = fb, method="chol", dfscale=1)

wind_sp.fd <- Data2fd(argvals = 1:(365*24), y = t(wind_sp[, -1]),
                      lambda = 10,
                      basisobj = fb, method="chol", dfscale=1)

## Mettre l'id_parc des courbes nom des courbes
fdc.fd$fdnames$reps <- fdc[, id_prod]
wind_sp.fd$fdnames$reps <- wind_sp[, id_prod]

residus <- get_linear_model_resuals(y_curves = fdc.fd, x_curves = wind_sp.fd, y.ncp = 5, x.ncp = 5)
```

## Step 6 : Detection on residual curves

### Step 1 : Compute depths

```{r}
#Tukey and Simplicial depths
f_tukey_depth <- residus[, -c("id_prod")] %>% functional_tukey_depth()

f_sdepth <- residus[, -c("id_prod")] %>% functional_simplicial_depth()

# Combine depths in data.table
fdc_depths <- data.table(id_prod = residus[, id_prod],
                         tdepth = f_tukey_depth,
                         sdepth = f_sdepth)
```

### Step 2 : detect anomaly

<!-- Voir s'il y a pas une meilleure option -->

```{r ref.label=c('chunk-depth-elbow'), echo = FALSE}

```

```{r ref.label=c('chunk-depth-analysis'), echo = FALSE}

```

<!-- According to Tukey depth... visible problem for simplicial depth -->

```{r, echo = FALSE}

# Curve 1
MostAtypical_1 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "63798", 
                                   main = "Wind farm '63798' : Most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC",
                                   group = "random-step1-res")

# Curve 2
MostAtypical_2  <- dyplotTimeSeries(data = dt_fdc_ws, 
                                    id_parc = "62363", 
                                    main = "Wind farm '62363' : Second most externe curve",
                                    col_date = "date", 
                                    col_series = "FDC", 
                                    color = "#900C3F",
                                    group = "random-step1-res")

# Curve 3
MostAtypical_3 <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "62362",
                                   main = "Wind farm '62362' : Third most externe curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#FFC300",
                                   group = "random-step1-res")

# Curve
Central_curves <- dyplotTimeSeries(data = dt_fdc_ws, 
                                   id_parc = "33238", 
                                   main = "Wind farm '33238' : Central curve",
                                   col_date = "date", 
                                   col_series = "FDC", 
                                   color = "#08B11F",
                                   group = "random-step1-res")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(Central_curves,
                                             MostAtypical_1, 
                                             MostAtypical_2, 
                                             MostAtypical_3), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```


<b>Depth contour</b>

```{r}
# Plot depth contour

df <- dt_fdc_ws[id_prod %in% "62362", .(id_prod, date, FDC)]

df <- df[, c("time", 
             "tdepth", 
             "sdepth") := .(difftime(date, as.POSIXct("2017-01-01 00:00:00 GMT"), units = "hours"),
                            tukey_depth(FDC),
                            simplicial_depth(FDC))
]

convex.hull0.25 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.25), 
                                          floor(length(FDC)*0.25),
                                          floor(length(FDC)*0.25) +1 )][chull(FDC)]

convex.hull0.5 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5), 
                                          floor(length(FDC)*0.5) +1 )][chull(FDC)]
convex.hull0.75 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75), 
                                          floor(length(FDC)*0.75) +1 )][chull(FDC)]
convex.hull0.975 <- df[
  rank(FDC, ties.method = "min") < ifelse(floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975), 
                                          floor(length(FDC)*0.975) +1 )][chull(FDC)]

p <- plot_ly(data = df, x= ~time, y = ~FDC, type = "scatter",
        marker = list(size = 4, color = ~tdepth),
        name = "Observed FDC"
) %>%
  layout(
    xaxis = ax,
    yaxis = ax,
    margin = list(pad = 20),
    legend = list(orientation = 'h')
  )


dc1 <- p %>% 
  add_polygons(x = convex.hull0.25[, time], 
               y = convex.hull0.25[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#111613 ",
                             line = list(color = "black", width = 2)),
               line = list(color = "#111613"),
               name = '0.25 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc2 <- p %>% 
  add_polygons(x = convex.hull0.5[, time], 
               y = convex.hull0.5[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#FFC300",
                             line = list(color = "black", width = 2)),
               line = list(color = "#FFC300"),
               name = '0.5 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")


dc3 <- p %>% 
  add_polygons(x = convex.hull0.75[, time], 
               y = convex.hull0.75[, FDC], 
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#7D3C98",
                             line = list(color = "black", width = 2)),
               line = list(color = "#7D3C98"),
               name = '0.75 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

dc4 <- p %>% 
  add_polygons(x = convex.hull0.975[, time], 
               y = convex.hull0.975[, FDC],
               fillcolor='rgba(255, 0, 0, 0.0)',
               marker = list(size = 1, color = "#15EE6E",
                             line = list(color = "black", width = 2)),
               line = list(color = "#15EE6E"),
               name = '0.975 th Q. surface') %>% 
  add_markers(x = df[which.max(tdepth), time], y = df[which.max(tdepth), FDC],
              marker = list(size = 10, color = "blue"),
              name = "Most depthest point")

# Combine curves on same graph
manipulateWidget::combineWidgets(list = list(dc1, dc2, dc3, dc4), 
                                 ncol = 2,
                                 height = "600px",
                                 width = "800px")

```


### Step 3 : Stop here
</div>